Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich Deep learning-based CSI feedback for RIS-assisted multi-user systems

\cite{mashhadi2020deepcmc}Proposes DeepCMC, a fully convolutional autoencoder with quantization and entropy coding blocks that achieves 3--5~dB lower NMSE than \cite{abe} at equivalent bit rates. Extends to a distributed version exploiting inter-user CSI correlations, reducing feedback overhead by 17--50\% for nearby users (<1m spacing) compared to single-user compression.

>>>>

\cite{mashhadi2020deepcmc}Proposes DeepCMC, a fully convolutional autoencoder with quantization and entropy coding blocks that achieves 3--5~dB lower NMSE than \cite{abe} at equivalent bit rates. Extends to a distributed version exploiting inter-user CSI correlations, reducing feedback overhead by 17--50\% for nearby users 
\begin{math}
	(<1m 
\end{math} 
spacing)
compared to single-user compression.
